---
title: "LDATS diagnostics/results exploration"
author: "Renata Diaz"
date: "5/28/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(LDATS)
```

### Paper data

```{r, eval = T}
load('diagnostics_526.Rdata')
```

Plot the LDA...

```{r, echo = F}
plot(selected)
```

Six topics seems like a lot!

Changepoint results:

```{r, echo = T}

summarize_cps(cps = changepoint$cps, prob = 0.95)

```


Changepoint diagnostics (not sure how to interpret these?)

```{r, echo = T}
changepoint$MCMCdiagnostics
```


Overall, it gets six topics and two changepoints, one in approximately 1989 and one in 2000 (both with large intervals). These line up with two of the changepoints from the paper. 

I'm curious about the big differences between this analysis and what was found in the paper. They're using exactly the same data, but getting different numbers of topics and changepoints. 

```{r}
rm(rodent_data, changepoint, selected)
```

### Granivores-only, control plots, longer time series

```{r}
load('diagnostics_526_controltimegraniv.Rdata')
```

Plot the LDA:

```{r, echo = F}
plot(selected)
```


Changepoint results:

```{r, echo = T}

summarize_cps(cps = changepoint$cps, prob = 0.95)

```


Changepoint diagnostics:

```{r, echo = T}
changepoint$MCMCdiagnostics
```


With only granivores, we get only 5 topics and approximately the same changepoints.

