---
title: "exploring 6 21"
author: "Renata Diaz"
date: "6/21/2018"
output: pdf_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Paper LDA model and LDATS changepoint

Load Christensen 2018 data and source paper functions: 

```{r load paper data and functions, eval = T}
library(topicmodels)
source('previous-work/AIC_model_selection.R')
source('previous-work/LDA-distance.R')



dat <- read.csv('paper_dat.csv', stringsAsFactors = F)

dates <- dat[,1]
dat <- dat[,2:22]
```


Run paper LDA model:

```{r run paper LDA, eval= F}
seeds = 2*seq(200)

# repeat LDA model fit and AIC calculation with a bunch of different seeds to test robustness of the analysis
best_ntopic = repeat_VEM(dat,
                         seeds,
                         topic_min=2,
                         topic_max=6)
```


Note that `repeat_VEM` returns, for each seed, the number of topics that produces the lowest AIC.


Histogram of best # of topics:

```{r LDA ntopics histogram, eval = F}
# histogram of how many seeds chose how many topics
hist(best_ntopic$k,breaks=c(0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5,9.5),xlab='best # of topics', main='')
```


Four topics is overwhelmingly the best (it is the best for the most seeds).


```{r select seed, eval = F}
ntopic = 4
# ==================================================================
# 2b. how different is species composition of 4 community-types when LDA is run with different seeds?
# ==================================================================
# get the best 100 seeds where 4 topics was the best LDA model
seeds_4topics = best_ntopic %>% 
  filter(k == 4) %>% 
  arrange(aic) %>% 
  head(100) %>% 
  pull(SEED)


# best seed for 4 is 206
# choose seed with highest log likelihood for all following analyses
#    (also produces plot of community composition for 'best' run compared to 'worst')
best_seed = calculate_LDA_distance(dat,seeds_4topics, k =4)
mean_dist = unlist(best_seed)[2]
max_dist = unlist(best_seed)[3]

best_seed
mean_dist
max_dist

```


Run the LDA model with the selected seed and number of topics.

```{r run LDA with chosen seed, eval = F}
ldamodel= LDA(dat,ntopics, control = list(seed = SEED),method='VEM')
```


Run the LDATS changepoint model with this LDA model.

Don't actually run this because it is time-consuming. Save and reload the changepoint model to look at it.

```{r run LDATS changepoint, eval = F}

library(LDATS)
source('functions/run_changepoint_model.R')
dat$date <- as.Date(dates)

changepoint = run_rodent_cpt(rodent_data = dat, selected = ldamodel,
                             changepoints_vector = c(2, 3, 4, 5, 6))

save(dat, ldamodel, changepoint, file = 'models/paperLDA_LDATScpt.Rdata')
```



Look at results.

```{r look at results, eval = T, echo = F}
library(LDATS)
library(dplyr)
library(ggplot2)
source('functions/lda_plot_function.R')

load('models/paperLDA_LDATScpt.Rdata')

plot(ldamodel)

plots = plot_community_composition_gg(community_composition(ldamodel), c(1:ldamodel@k), ylim = c(0, 1))

plots

summarize_cps(changepoint$cps, prob = 0.95)

changepoint$MCMCdiagnostics


```
## Looking at various chains in changepoint models

This will take more memory, because I need to fiddle around with the select_changepoint_model procedure.


