---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/renatadiaz/Documents/GitHub/weecology/LDA-kratplots")
knitr::opts_chunk$set(echo = TRUE)
```


```{r load packages and functions, include = F}
library(LDATS)
library(dplyr)
library(tidyr)
library(ggplot2)
source('functions/plots_from_ldats.R')
source('functions/convert_summary_to_dates.R')
```

# With weights all equal

```{r load wts1, echo = F}
load('models/time_steps/ctrl_time_gran_wt1.Rdata')

rodent_data_ctrl = rodent_data
time_data_ctrl = time_data
changepoint_ctrl = changepoint
changepoint_models_ctrl = changepoint_models
selected_ctrl = selected

rm(rodent_data, time_data, changepoint, changepoint_models, selected)

load('models/time_steps/excl_time_gran_wt1.Rdata')

rodent_data_excl = rodent_data
time_data_excl = time_data
changepoint_excl = changepoint
changepoint_models_excl = changepoint_models
selected_excl = selected

rm(rodent_data, time_data, changepoint, changepoint_models, selected)

```

## LDA models

#### Control plots LDA
```{r plot control LDA wt 1,echo = F, fig.height = 4, fig.width = 7}
plot_lda_edited(selected_ctrl, time_data_ctrl$date)
```

#### Exclosures LDA
```{r plot excl LDA wt 1, echo = F, fig.height = 4, fig.width = 7}
plot_lda_edited(selected_excl, time_data_excl$date)
```


## Changepoint models

#### Selected changepoint model for control plots

```{r cpt summary ctrl wt 1, echo = F}

ctrl_cpt_summary_dates <- convert_summary_to_dates(changepoint_ctrl, time_data_ctrl)

ctrl_cpt_summary_dates
```

```{r cpt plot ctrl wt 1, echo = F}

cps_gathered_ctrl = tidyr::gather(as.data.frame(changepoint_ctrl$cps), key = 'cpt', value = 'year_number', 1:changepoint_ctrl$nchangepoints)

cps_years <- select(rodent_data_ctrl, date) %>%
  mutate(date = format(as.Date(date, format="%d/%m/%Y"),'%Y')) %>%
  mutate(date = as.numeric(date)) %>%
  mutate(year_number = row_number()) 

cps_gathered_ctrl <- left_join(cps_gathered_ctrl, cps_years, by = 'year_number')

cps_hist_ctrl <- ggplot(cps_gathered_ctrl, aes(x=date, fill = cpt)) + 
  geom_histogram() +
  theme_bw() + 
  labs(title = 'Changepoint estimates - control')

cps_hist_ctrl

cps_ctrl <- cps_gathered_ctrl %>%
  mutate(treatment = 'control')

```

#### Deviances for different numbers of changepoints - control
```{r ctrl wt 1 deviances, echo = F}

ctrl_deviances = list(NULL)

for(i in 1:length(changepoint_models_ctrl)){
  ctrl_deviances[i] <- changepoint_models_ctrl[[i]]$deviance
  names(ctrl_deviances)[i] <- changepoint_models_ctrl[[i]]$nchangepoints
}


print(ctrl_deviances)

```


#### Selected changepoint model for exclosure plots

```{r cpt summary excl wt 1, echo = F}

excl_cpt_summary_dates <- convert_summary_to_dates(changepoint_excl, time_data_excl)

excl_cpt_summary_dates
```

```{r cpt plot excl wt 1, echo = F}

cps_gathered_excl = tidyr::gather(as.data.frame(changepoint_excl$cps), key = 'cpt', value = 'year_number', 1:changepoint_excl$nchangepoints)

cps_years <- select(rodent_data_excl, date) %>%
  mutate(date = format(as.Date(date, format="%d/%m/%Y"),'%Y')) %>%
  mutate(date = as.numeric(date)) %>%
  mutate(year_number = row_number()) 

cps_gathered_excl <- left_join(cps_gathered_excl, cps_years, by = 'year_number')

cps_hist_excl <- ggplot(cps_gathered_excl, aes(x=date, fill = cpt)) + 
  geom_histogram() +
  theme_bw() + 
  labs(title = 'Changepoint estimates - exclosure')

cps_hist_excl

cps_excl <- cps_gathered_excl %>%
  mutate(treatment = 'exclosure')

```

#### Deviances for different numbers of changepoints - exclosure
```{r excl wt 1 deviances, echo = F}

excl_deviances = list(NULL)

for(i in 1:length(changepoint_models_excl)){
  excl_deviances[i] <- changepoint_models_excl[[i]]$deviance
  names(excl_deviances)[i] <- changepoint_models_excl[[i]]$nchangepoints
}


print(excl_deviances)

```

# With weights proportional to rodents captured


```{r load wtsprop, echo = F}
load('models/time_steps/ctrl_time_gran_wtprop.Rdata')

rodent_data_ctrl = rodent_data
time_data_ctrl = time_data
changepoint_ctrl = changepoint
changepoint_models_ctrl = changepoint_models
selected_ctrl = selected

rm(rodent_data, time_data, changepoint, changepoint_models, selected)

load('models/time_steps/excl_time_gran_wtprop.Rdata')

rodent_data_excl = rodent_data
time_data_excl = time_data
changepoint_excl = changepoint
changepoint_models_excl = changepoint_models
selected_excl = selected

rm(rodent_data, time_data, changepoint, changepoint_models, selected)

```

## LDA models

#### Control plots LDA
```{r plot control LDA wt prop,echo = F, fig.height = 4, fig.width = 7}
plot_lda_edited(selected_ctrl, time_data_ctrl$date)
```

#### Exclosures LDA
```{r plot excl LDA wt prop, echo = F, fig.height = 4, fig.width = 7}
plot_lda_edited(selected_excl, time_data_excl$date)
```


## Changepoint models

#### Selected changepoint model for control plots

```{r cpt summary ctrl wt prop, echo = F}

ctrl_cpt_summary_dates <- convert_summary_to_dates(changepoint_ctrl, time_data_ctrl)

ctrl_cpt_summary_dates

```

```{r cpt plot ctrl wt prop, echo = F}

cps_gathered_ctrl = tidyr::gather(as.data.frame(changepoint_ctrl$cps), key = 'cpt', value = 'year_number', 1:changepoint_ctrl$nchangepoints)

cps_years <- select(rodent_data_ctrl, date) %>%
  mutate(date = format(as.Date(date, format="%d/%m/%Y"),'%Y')) %>%
  mutate(date = as.numeric(date)) %>%
  mutate(year_number = row_number()) 

cps_gathered_ctrl <- left_join(cps_gathered_ctrl, cps_years, by = 'year_number')

cps_hist_ctrl <- ggplot(cps_gathered_ctrl, aes(x=date, fill = cpt)) + 
  geom_histogram() +
  theme_bw() + 
  labs(title = 'Changepoint estimates - control')

cps_hist_ctrl

cps_ctrl <- cps_gathered_ctrl %>%
  mutate(treatment = 'control')

```

#### Deviances for different numbers of changepoints - control
```{r ctrl wt prop deviances, echo = F}

ctrl_deviances = list(NULL)

for(i in 1:length(changepoint_models_ctrl)){
  ctrl_deviances[i] <- changepoint_models_ctrl[[i]]$deviance
  names(ctrl_deviances)[i] <- changepoint_models_ctrl[[i]]$nchangepoints
}


print(ctrl_deviances)

```


#### Selected changepoint model for exclosure plots

```{r cpt summary excl wt prop, echo = F}

excl_cpt_summary_dates <- convert_summary_to_dates(changepoint_excl, time_data_excl)

excl_cpt_summary_dates
```

```{r cpt plot excl wt prop, echo = F}

cps_gathered_excl = tidyr::gather(as.data.frame(changepoint_excl$cps), key = 'cpt', value = 'year_number', 1:changepoint_excl$nchangepoints)

cps_years <- select(rodent_data_excl, date) %>%
  mutate(date = format(as.Date(date, format="%d/%m/%Y"),'%Y')) %>%
  mutate(date = as.numeric(date)) %>%
  mutate(year_number = row_number()) 

cps_gathered_excl <- left_join(cps_gathered_excl, cps_years, by = 'year_number')

cps_hist_excl <- ggplot(cps_gathered_excl, aes(x=date, fill = cpt)) + 
  geom_histogram() +
  theme_bw() + 
  labs(title = 'Changepoint estimates - exclosure')

cps_hist_excl

cps_excl <- cps_gathered_excl %>%
  mutate(treatment = 'exclosure')

```

#### Deviances for different numbers of changepoints - exclosure
```{r excl wt prop deviances, echo = F}

excl_deviances = list(NULL)

for(i in 1:length(changepoint_models_excl)){
  excl_deviances[i] <- changepoint_models_excl[[i]]$deviance
  names(excl_deviances)[i] <- changepoint_models_excl[[i]]$nchangepoints
}


print(excl_deviances)

```
